Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-14 ms.tex
mainly bandpass correction discussion

%list of figures : 
% posterior surface for some pixel, with samples from markov chain overplotted
%    --> also overplot output best-fit (T,I545) and unctertainty estimate
% plot for some set of pixels of SED overlaid with best-fit two-component model
%    --> done in Python instead of IDL
%    --> overlay 
% plot of resulting T2 and tau
% plots of full-sky residuals relative to our model ?
%  ---> and for lower-frequency bands to emphasize that FDS99 is better for
%       extrapolating towards mm wavelengths
% zoom-in of region with interesting dust showing :
%  SFD T map, two-component T map, Planck team one-component T map

@@

Some of the maps in native format are provided in thermodynamic $\delta T$, 
while others are provided in units of MJy/sr. Before performing any fits, 
we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse} and the document ``HFI-unit conversion and colour correction instructions v1.2''.

%i think it's table 5 that I specifically want to cite within the ``spectral
%response'' paper, but i need to check that those values are consistent
% with the ones i actually used from the other document

@@

\subsection{Finite Bandpass Correction}

@@

\begin{equation}
M_{\nu} \propto f_{1}q_{1}(\nu/\nu_{0})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)
\end{equation}

@@

\subsubsection{Ignoring 217 GHz}
The \cite{planckdust} result used only XX, YY, ZZ, 3000 GHz. When we 
repeat our analysis ignoring 217 GHz, so that we are using the same
set of frequencies, we find that no major changes arise. This actually
should be done/investigated though.

>>>>

%list of figures : 
% posterior surface for some pixel, with samples from markov chain overplotted
%    --> also overplot output best-fit (T,I545) and unctertainty estimate
% plot for some set of pixels of SED overlaid with best-fit two-component model
%    --> done in Python instead of IDL
%    --> overlay 
% plot of resulting T2 and tau
% plots of full-sky residuals relative to our model ?
%  ---> and for lower-frequency bands to emphasize that FDS99 is better for
%       extrapolating towards mm wavelengths
% zoom-in of region with interesting dust showing :
%  SFD T map, two-component T map, Planck team one-component T map
%      good spot is in polaris, centered on (lgal,bgal) ~ (112, 20)

@@

Some of the maps in native format are provided in thermodynamic $\delta T$, 
while others are provided in units of MJy/sr. Before performing any fits, 
we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse}.

%i think it's table 5 that I specifically want to cite within the ``spectral
%response'' paper, but i need to check that those values are consistent
% with the ones i actually used from the other document ``HFI-unit conversion 
%and colour correction instructions v1.2''

@@

\subsection{Finite Bandpass Correction}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. But in reality
we are comparing to broad bands typically hundreds of GHz wide. The shape of 
model spectrum $M_{\nu}$ is only dependent upon one parameter: the hot
dust temperature $T_2$. We have therefore computed bandpass correction factors
$b_{\nu_i}$ such that $M_{\nu_i}b_{\nu_i}$ is the predicted observation for the
\PLANCK~or \IRAS~band of interest. We have used the \PLANCK~transmission 
curves provided in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. 
For 3000 GHz, we have used the \IRAS~bandpass, following the treatment of
\cite{planckdust}. We note that it is not clear which bandpass should
properly be considered for the IRAS/DIRBE composite 100$\mu$m maps used in 
this analysis (here SFD \verb|i100|) and that of \cite{planckdust}.

% check that RIMO file i've used is actually the most up-to-date version

@@

\begin{equation}
M_{\nu} \propto f_{1}q_{1}(\frac{\nu}{\nu_{0}})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\frac{\nu}{\nu_0})^{\beta_2}B_{\nu}(T_2)
\end{equation}

@@

\subsubsection{Omitting 217 GHz}
The \cite{planckdust} result used only XX, YY, ZZ, 3000 GHz. When we 
repeat our analysis ignoring 217 GHz, so that we are using the same
set of frequencies, we find that no major changes arise. This actually
should be done/investigated though.
